Ms 1

### 2017-05-23 ms1/ms1_display.Rmd
updated to new tables

```{r global_options, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE,
                      error=FALSE, autodep=TRUE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace)
```

@@

```{r}
read_tsv('tables/tbl_totals.tsv') %>%
  mutate_at(vars(n_bene, n_pde), function(x) prettyNum(x, big.mark=',')) %>%
  mutate_at(vars(cpkp), function(x) round(x)) %>%
  kable
```

# Claims against age

```{r claims_by_age}
claims_by_age = read_tsv('tables/tbl_claims_by_age.tsv')

claims_by_age %>%
  filter(year==2011, !(group=='no_cc' & age < 67)) %>%
  ggplot(aes(x=age,
             y=mean_n_claims,
             ymin=mean_n_claims-sem_n_claims,
             ymax=mean_n_claims+sem_n_claims,
             color=group)) +
  geom_smooth(method='lm', se=F, size=0.5) +
  geom_point() +
  geom_linerange() +
  scale_x_continuous(breaks=c(66, 70, 80, 90, 96)) +
  scale_y_continuous(breaks=c(0.0, 1.0, 1.5, 2.0)) +
  theme_minimal()

lm_ci = function(df, formula) {
  lm(formula, data=df) %>%
    tidy %>%
    mutate(ci=1.96*std.error, cil=estimate-ci, ciu=estimate+ci)
}

claims_by_age %>%
  group_by(group) %>%
  do(lm_ci(., mean_n_claims ~ age)) %>%
  filter(term=='age') %>%
  select(group, estimate, cil, ciu) %>%
  kable
```

@@

## Claims by class

```{r}
read_tsv('tables/tbl_claims_by_class.tsv') %>%
  select(antibiotic_class, year, cpkp) %>%
  spread(year, cpkp) %>%
  mutate(antibiotic_class=if_else(row_number(desc(`2011`)) < 10, antibiotic_class, 'other')) %>%
  group_by(antibiotic_class) %>%
  summarize_all(sum) %>%
  mutate_at(vars(-antibiotic_class), round) %>%
  arrange(desc(`2011`)) %>%
  kable
```

## Most-prescribed antibiotics

```{r}
claims_by_abx = read_tsv('tables/tbl_claims_by_abx.tsv')

top_abx = claims_by_abx %>%
  filter(year==2011) %>%
  filter(row_number(desc(cpkp)) < 10) %$%
  antibiotic

claims_by_abx %>%
  filter(antibiotic %in% top_abx) %>%
  select(antibiotic, year, cpkp) %>%
  spread(year, cpkp) %>%
  mutate_at(vars(-antibiotic), round) %>%
  arrange(desc(`2011`)) %>%
  kable
```

@@

```{r}
read_tsv('tables/tbl_all_condition_model.tsv') %>%
  mutate(term=stringr::str_replace(term, 'TRUE$', '')) %>%
  left_join(condition_names, by=c('term'='condition')) %>%
  mutate(term=if_else(is.na(condition_name), term, condition_name),
         log10.adj.p.value=log10(p.adjust(p.value, method='BH'))) %>%
  select(term, estimate, p.value, log10.adj.p.value) %>%
  filter(term != '(Intercept)') %>%
  arrange(desc(estimate)) %>%
  kable
```

# Single-condition models

```{r}
read_tsv('tables/tbl_single_condition_models.tsv') %>%
  select(condition, term, estimate) %>%
  spread(term, estimate) %>%
  kable
```

>>>>

```{r global_options, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE,
                      error=FALSE, autodep=TRUE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace, str_detect)

pctize = function(df, denom_name) {
  for (n_name in Filter(function(x) str_detect(x, '^n_'), names(df))) {
    pct_name = str_replace(n_name, '^n_', 'pct_')
    df[[pct_name]] = df[[n_name]] / df[[denom_name]] * 100
  }
  df
}
```

@@

```{r}
read_tsv('tables/tbl_totals.tsv') %>%
  pctize('n_bene') %>%
  select(year, n_bene, mean_age, mean_n_cc,
         pct_female, pct_white, pct_dual,
         pct_region_south, pct_region_midwest, pct_region_northeast, pct_region_west) %>%
  mutate_at(vars(starts_with('pct_')), function(x) round(x, digits=1)) %>%
  mutate(n_bene=prettyNum(n_bene, big.mark=','),
         mean_age=round(mean_age, digits=1),
         mean_n_cc=round(mean_n_cc, digits=2)) %>%
  gather('var', 'val', -year) %>% spread(year, val) %>% # transpose
  kable
```

@@

## Claims by abx

```{r}
dat = read_tsv('tables/tbl_claims_by_abx.tsv')
totals = dat %>% group_by(year) %>% summarize(cpkp=sum(cpkp)) %>% mutate(antibiotic='all')
top_abx = dat %>%
  group_by(antibiotic) %>%
  summarize(cpkp=mean(cpkp)) %>%
  arrange(desc(cpkp)) %$%
  head(antibiotic, 10)

x = dat %>%
  select(antibiotic, year, cpkp) %>%
  filter(antibiotic %in% top_abx) %>%
  bind_rows(totals) %>%
  mutate(antibiotic=factor(antibiotic, levels=c('all', top_abx)))

x %>%
  mutate(cpkp=round(cpkp)) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>%
  kable

x %>% ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~ antibiotic, ncol=3, scales='free_y') +
  geom_point() + geom_line() +
  theme_minimal()
```

## Claims by age group

```{r claims_by_age}
read_tsv('tables/tbl_claims_by_age.tsv') %>%
  mutate(cpkp=round(cpkp)) %>%
  select(year, age_group, cpkp) %>%
  spread(year, cpkp) %>%
  kable
```

@@

```{r, eval=FALSE}
read_tsv('tables/tbl_all_condition_model.tsv') %>%
  mutate(term=stringr::str_replace(term, 'TRUE$', '')) %>%
  left_join(condition_names, by=c('term'='condition')) %>%
  mutate(term=if_else(is.na(condition_name), term, condition_name),
         log10.adj.p.value=log10(p.adjust(p.value, method='BH'))) %>%
  select(term, estimate, p.value, log10.adj.p.value) %>%
  filter(term != '(Intercept)') %>%
  arrange(desc(estimate)) %>%
  kable
```
